Inference of Bifurcations\\with Differentiable Continuation

### 2021-05-17 docs/appendix.tex
Updates from Overleaf

Figure \ref{fig:determinant-field} reveals that $\Det=0$ is also a level set and that the intersection with level set $\rates(z)=0$ defines the bifurcations at specific parameter $\theta$. In this particular setting we can see that the tangent field $\tangent(z)$ only folds when $\Det=0$. Plotting the value of the determinant along $\rates(z)=0$ from Figure \ref{fig:determinant-field} would give rise to Figures \ref{fig:saddle-node} and \ref{fig:pitchfork}. The directional derivative of the determinant $\Det$ along the tangent field $\tangent(z)$ is defined as

>>>>

Figure \ref{fig:determinant-field} reveals that $\Det=0$ is also a level set and that the intersection with level set $\rates(z)=0$ defines the bifurcations at specific parameter $\theta$. In this particular setting we can see that the tangent field $\tangent(z)$ only folds when $\Det=0$. Plotting the value of the determinant along $\rates(z)=0$ from Figure \ref{fig:determinant-field} would give rise to Figures \ref{fig:minimal-models}. The directional derivative of the determinant $\Det$ along the tangent field $\tangent(z)$ is defined as
